---
title: "R code for more difficult problems"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```


# FizzBuzz Problem
#### Below see the R code for the FizzBuzz problem, in which every number from 1-100 that is divisible by 3 is replaced by "Fizz" and every number divisible by 5 is replaced with "Bizz". Numbers that are divisible by both are replaced with "FizzBuzz".


```{r}
num <-1
seq<- c(1:100)
for(i in seq) {
  if (num%%3==0 && num%%5==0){
      seq[num]<-"FizzBuzz"
    }
  else if (num%%3==0 & num%%5!=0){
      seq[num]<-"Fizz"
    }
  else if (num%%3!=0 & num%%5==0){
      seq[num]<-"Buzz"
    }
  else {
      seq[num]<-num
    }
  num <- num+1
}
paste(as.character(seq),"",collapse=", ",sep="")
##print(seq)
```

# Snakes & Ladders
#### Below see the R code that simulates the Snakes and Ladders Board found at https://crumplab.github.io/programmingforpsych/programming-challenges-i-learning-the-fundamentals.html#harder-problems and estimates the average number of dice rolls needed to successfully complete the game.


```{r}
sum<-0
for(i in 1:1000) {
    CurrentSpace<-1
    diceRolls<-0
    while(CurrentSpace<26){
        diceNum<-sample(c(1,2,3,4,5,6),1)
        diceRolls <- diceRolls +1
        CurrentSpace <- CurrentSpace + diceNum
        if(CurrentSpace==3) {CurrentSpace<- 11}
        if(CurrentSpace==6) {CurrentSpace<- 17}
        if(CurrentSpace==9) {CurrentSpace<- 18}
        if(CurrentSpace==10) {CurrentSpace<-12}
        if(CurrentSpace==19) {CurrentSpace<-8}
        if(CurrentSpace==22) {CurrentSpace<-20}
        if(CurrentSpace==24) {CurrentSpace<-16}
    }
    sum <- sum +diceRolls
}
AveDiceRolls <- sum/1000
print(capture.output(cat('Average Dice Rolls for 1000 trials: ', AveDiceRolls)))
```



